\documentclass[letterpaper,margin,line]{RES}
%\usepackage{helvetica} % uses helvetica postscript font (download %helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{1pt}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
% This is my line
\def\myline{\\\rule{\textwidth}{1pt}\\}
\def\mmmyline{\rule{\textwidth}{1pt}\\}
\def\mmyline{\\\rule{\textwidth}{.5pt}\\}

\begin{document}

\name{Rishi Agrawal\vspace*{.1in} \small{\it M.S, B.E, Computer Science}}

\begin{resume}
\section{\sc Contact Information}
\begin{tabular}{@{}p{2in}p{4in}}
102,                      & {\it Mobile:}  (+91) 9673002472 \\            
Richmond Park,      & {\it E-mail:}  rishi.b.agrawal@gmail.com \\       
Behind Central Bank,          &  \\ 
Baner Road, Baner,          &  \\ 
Pune-411045, Maharashtra    & \\ 
\end{tabular}
\mmmyline

\section{\sc Personal Information}
\begin{tabular}{@{}p{2in}p{4in}}
Date of Birth  & 5th February, 1986 \\            
Nationality    & Indian  \\            
Martial Status & Married \\            
Home Town      & Jamshedpur, Jharkhand\\
Passport valid till 19/07/2016.\\ 
USA B1 Business Visa valid till Oct, 2024
\end{tabular}
\mmmyline

{ \bf 	
\section{\sc Computer Skills}
\vspace{.04in}}

\begin{tabular}{@{}p{2in}p{4in}}
{\bf Languages}                             & C, Python \\
{\bf Tools}                                 & gcc, make, Sphinx, VirtualBox \\
{\bf Debugging Tools}                       & gdb, System Tap, Crash, strace, ltrace \\
{\bf Performance Tools}                     & iozone, specsfs, iperf, blktrace \\
{\bf Scripting Languages}                   & Bash \\
{\bf Operating Systems}                     & Linux Kernel \\
\end{tabular}

\section{\sc Professional Experience }



{\sl \bf Stealth Mode Startup } \hfill May 2015 to Oct 2015 \\
		 Engineering Lead
       \myline
	   Cannot disclose the organization's work domain due to a Non Disclosure
	   Agreement.


{ \bf Responsibilities}
\mmyline

{ \bf Engineering Lead  }
	\begin{list2}
	\item Wrote a Linux Block Device Driver to store data with an embedded Key-Value based Database over Kernel Sockets.
    \item Worked on finding innovative solutions on high performance hardware.
	\end{list2}

{\sl \bf Agiliad Technologies } \hfill Sep 2014 to May 2015 \\
		 Technical Lead, Storage Group
       \myline

		Agiliad is the next generation of Product Engineering Services -
		Collaborative Innovation. As a service based organization they help
		product companies succeed by enabling collaborative innovation across
		the boundaries of domain, geography and expertise.

		They currently are working on revolutionary new products and ideas in
		Medical/Healthcare, Industrial Automation and Storage/Data/Cloud
		technologies. 

{ \bf Responsibilities}
\mmyline

{ \bf Team Lead  }
	\begin{list2}
    \item Worked as a developer in a hyper converged appliance.
    \item Training of new hires in the project.
	\item Setting up the team with right processes in place.\end{list2}


{\sl \bf Symantec SNAS (previously FileStore)} \hfill Feb 2013 to Aug 2014 and July 2009 to Feb 2012 \\
		 Software Engineer, Storage \& Availability Management
		 Group
       \myline
       Symantec SNAS is a clustered NAS solution designed to meet the high
       performance, scalability and comprehensive data protection requirements
       for a range of applications from enterprise file serving to emerging
       web-based services. Symantec SNAS is built upon the industry-leading
       Symantec Storage Foundation stack which enables SSNAS to provide the
       solid and reliable performance and high availability that is expected in
       today’s high performance storage environments.

{ \bf Responsibilities}
\mmyline

{ \bf Samba Integration in SSNAS  }
	\begin{list2}
    \item Integrated the Samba stack in the product which enables the users to access files over CIFS.
    \item Lead initiative in improving the test suite to cover wider and customer based scenarios.\end{list2}

{ \bf Optimization of Anti Virus Feature }
    \begin{list2}
    \item Implemented and optimized the filter which excludes the files based on mount-points and file extensions in the kernel space.
    \end{list2}

{ \bf Client Escalations }
    \begin{list2}
    \item Handled escalation and bugs realated to storage subsection.
    \end{list2}


{ \bf Owner of storage section in product }
    \begin{list2}
    \item Integrated SCST (http://scst.sourceforge.net/) into FileStore to add Unified Storage capablities.
    \item Hands on experience with Veritas File System and Veritas Volume Manager.
    \item Shouldered responsibility of features such as Snapshots, File Change Log, Dynamic Storage Tiering, IO Fencing, Volume Management, Dynamic Multi-pathing.
    \item Mentored a 4 member team of developers in China to handle storage related issues and development of new features.
    \item Organized product training to new members joining the Dev and QA teams across various development centres.
    \end{list2}

{ \bf Others }
    \begin{list2}
	\item Evaluated the product processes and operations from end to end and gave a presentation on our short comings. My suggestions for improvement were widely appreciated by the global team.
    \item Automated cluster creation using VMware platform, this helped the development and the testing team to save 90\% of their time.  
    \item Mentored and interviewed candidates, conducted training program for new joinees.
    \item Took initiative towards forming processes to facilitate CVS tracking over multiple releases and branches. This involved studying processes existing in other teams, development and optimization of processes for my team. This brought discipline to the incident management and resulted into time savings by Dev/QA and Doc team.
    \item Part of release team, handled release responsibilities for entire release cycle.
    \item Worked on Cisco SAN Switches, NetApp and Hitachi arrays.
    \end{list2}

{\sl \bf Nvidia} \hfill Nov 2012 to Feb 2013 \\
		 Software Engineer, Full Stack Frame Work
       \myline
       Full Stack FrameWork is a virtualization tool which simulates the 
       graphic silicon and enables the chip designers to run verification 
       tools in simulated environment. This helps the designers to verify 
       the correctness of the graphic silicon and associated device.

{ \bf Responsibilities}
\mmyline
	\begin{list2}
    \item Enhanced the tool to suite the requirements and feature set of freshly released chips.
    \item Single point of contact for the team.
    \end{list2}

\section{\sc Professional Experience }
{\sl \bf Veritas File System} \hfill Mar 2012 to  Oct 2012 \\
		 Software Engineer, Storage \& Availability Management
		 Group
       \myline
       Veritas File System (VxFS) was the first commercial journaling file system. With
       journaling, metadata changes are first written to a log, then to disk.
       It is extent-based, intent logging file system and is designed for use
       in operating environments that require high performance and availability and
       deals with large amounts of data.

{ \bf Responsibilities}
\mmyline
	\begin{list2}
    \item Worked as a kernel developer in a cross-geo development team involved in customer facing engineering work.
    \item Responsible for designing and implementing new features, enhancing the existing features, writing test cases.
    \item As part of Pune escalation team, handling issues in India, attending calls with customers and support staff, working on customer issues. 
    \end{list2}

\section{\sc Open Source Contributions }
{\sl \bf Online Hierarchical Storage Manager } \hfill Nov 2008 to June 2009 
\myline
    OHSM is Online Hierarchical Storage Manager for Linux which offers policy based transparent movement of data from one storage class to other. Also being the first attempt towards an enterprise level open source data manager, it provides a base platform for all further developments in the similar area.

    Whitepaper: https://www.kernel.org/doc/ols/2009/ols2009-pages-263-274.pdf    

{\bf Features }
\mmyline
\begin{list2}
    \item   HSM for the Linux framework supporting ext2/ext3 file systems.
    \item   Initial file creation based on policies written in XML.
    \item   Non-disruptive, policy based relocation.
    \item   Ability to define storage classes.
    \item   Tricky Copy Algorithm.
    \end{list2} 

{\bf Responsibilities }
\mmyline
\begin{list2}
    \item     Lead a team of five people.
    \item     Involved in development life cycle with initial analysis and the design framework.
    \item     Coding the driver unit, XML parser and the ioctl interface.
    \item     Unit and Integration Testing.
    \end{list2}

\section{\sc Achievements, Awards and Interests}
\begin{list2}
\item Twice awarded with "Applause Award", Symantec for improving the quality of product.
\item Co-authored a paper “Online Hierarchical Storage Manager in Linux”
    \begin{list2}
    \item The paper was selected at Ottawa Linux Symposium, 2009.
    \item Third Prize at Cognizance '09, held at Indian Institute of Technology, Roorkee.
    \item Consolation prize at Techkriti '09, held at Indian Institute of Technology, Kanpur.
    \item First Prize at INNOVATION 2k9 held at Cummins College of Engineering, Pune.
    \item Second Prize at Jishin '09, held at Bharti Vidyapeeth College of Engineering for Women, Pune.
    \item Third Prize at Techno Dream '09, held at Maharashtra Academy of Engineering, Alandi.
     \end{list2}   
\item First Position in C/C++ programming contest at Technodium '07, Maharashtra Academy of Engineering, Alandi in 2007.
\item Best Programmer Award by MAE Technical Alumni at Maharashtra Academy of Engineering, Alandi in 2007.
\end{list2}

\section{\sc Other Activities}
\begin{list2}
\item Conducted workshops on Linux Programming in organizations and colleges.
\item Mentored students in Linux Kernel Projects.
\item Participated in SAMG Premier League (cricket tournament) 2009, '10(lead) and '11.
\item Worked for NGO Nai Disha. \\
\end{list2}

\section{\sc Education}
\begin{tabular}{@{}p{4in}p{.75in}p{.75in}}
{\bf Master of Science, Computer Science }              &  2011 &  69.7 \%  \\
Sikkim Manipal Distance Education                       &       & \\        \hline \\ 
{\bf B.E in Computer Science and Engineering }          &  2009 &  69.9 \%     \\
University Of Pune, Pune                                &       & \\ \hline \\ 
{\bf Higher Secondary }                                 &  2005 &  67.2 \%   \\       
Narbheram Hansraj English School, \it Board: ISC        &       &       
\\ \hline     \\
{\bf High School }                                      &  2003 &  80.0 \%   \\    
Narbheram Hansraj English School, \it Board: ICSE                       &       &            \\
\end{tabular}

\end{resume}
\end{document}

